Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
Update cospans.tex

@@

>>>>

\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})$};
\node (B) at (0,-0.5) {$d_{\lH(M)}$};
\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\lH(1_\A)}}\otimes d_{\lH(M)})$};
\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\lH(1_\A \otimes M)})$};

@@

where $$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\A'}} \otimes d_{\lH(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \A'$ commutes. The other square involving the right unitors $r$ and $r'$ is similar. Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\lH$ is strong.
